A Modular Framework for Developing, Deploying, and Evaluating Game-Theoretic Strategy Design Exercises

### 2018-05-04 paper.tex
Start Approach

>>>>

\section*{Approach}
Throughout the course of developing this framework, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester.
That is, in order to develop a reusable toolchain for building strategy design exercises, I have developed strategy design exercises to inform the design and development of a reusable toolchain.
